---
title: "linear_regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linear_regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Some R packages that need to setup. The first one called "linreg" is my package.
The package consists of some useful methods in linear regression to get significant statistics.
It mainly includes these statistics for people to analyze a model:
1. Standard error; 
2. R_squared value; 
3. t-statistics;
4. p-value; 
5. Estimation of coefficients
```{r setup}
library(linreg)
library(tidyr)
library(car)
library(bench)
```
##Function usage Tutorial
Here are the details of the use of my method in package:
```{r}
## Import data set to examine
## I use the data set of mtcars to demonstrate how to use the package in detail:
dt <- mtcars
```

```{r}
## Multiple linear regression with intercept
## I choose "cyl", "disp" in mtcars as predictor X, and "mpg" as responsen Y.
model_car <- linear_regression(X = dt[,c(2,3)],
                              Y = dt$mpg
                              )
```



```{r}
##The summary of the model
model_lm <- lm(data = dt, formula = mpg~cyl+disp)
summary(model_lm)
```

```{r}
anova(model_lm)
```

## Correctness and Efficiency Check

```{r}
### Simulate data
set.seed(800)
#Generate the independent variable and the error
x1=rnorm(10000,100,14)
x2=rnorm(10000,200,34)
error=rnorm(10000,0,24)
#Generate the dependent variable
y1=100-(4*x1)+(8*x2)+error
testdata <- as.data.frame(cbind(y1,x1,x2))
```

#### Model Construction
```{r}
## The regression function in my package
model_new <- linear_regression(X = testdata[,c(2,3)],
                              Y = testdata[1])
cat("")
## The base regression function
model_base <- lm(data=testdata, formula =  y1~x1+x2)
summary(model_base)
```
#### Method Correctness and Efficiency
Compare the correctness of the code by using 'all.equal' fuction
Compare the speed of the code by using 'bench:mark()' function:
```{r}
## Aiming to round the error in these two calculations, we will save up to 10 digits to examine the correctness and efficiency.
all.equal(round(model_new[[1]][,1], digits=10),
          round(model_base$coefficients, digits=10))
cat("")
bm <- bench::mark(round(model_new[[1]][,1], digits=10),
            round(model_base$coefficients, digits=10))
summary(bm)
```
From the results of these two functions, we can find that the method of my package is basically correct and more faster than the existed linear regression function in R, which meets the standard of correctness and efficiency.




















